---
title       : BOTANICAL CLOCK
subtitle    : by Carolus Linnaeus
author      : Urli2016
job         : Reproducible Presentation
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

##### BOTANICAL CLOCK, GENERAL INFORMATION, Slide 1
```{r}
library(shiny)
library(ggplot2)
library(knitr)
library(markdown)
Flowers <- read.csv("Flowers.csv")
```

###### Carolus Linnaeus has been an awarded scientist in the 17th century and he had the hypothetical plan to plant a clock ruled by the opening and closing times of different flowers. He had a list by his own, I only took a few and created my own csv-file called 'Flowers.csv' ordered by opening times.

---

##### BOTANICAL CLOCK, DESCRIPTION, Slide 2
###### I decided to use a ShinyUI(navbarPage) as it has not been used in the class. One of our tasks was to implement a widget. I created a selectbox in order to show the botanical names of these flowers in latin and therefore recognizable by scientists all over the world. I also added a Markdown-File including the biography of Carolus Linnaeus and a rough description of the flowers.

```{r}
shinyUI(navbarPage("BOTANICAL CLOCK",
                   tabPanel("Description",
                            sidebarLayout(
                                 sidebarPanel(
                                 selectInput("select", label = h3("Botanical Names of Flowers"),                                                                         choices = list("Yellow Goats Beard" = "Tragopogon pratensis", "Rough Hawkbit" = "Leontodon hispidus", "Narrow Leaf Hawksbeard" = "Crepis tectorum", "Sow Thistle" = "Sonchus oleraceus", "Dandelion" = "Taraxacum officinale Weber", "Hawksbeard" = "Crepis alpina", "False Sow Thistle" = "Reichardia tingitana", "Spotted Cats Ear" = "Hypochaeris maculata", "Canadian Hawkweed" = "Hieracium umbellatum", "Marsh Sow Thistle" = "Sonchus palustris", "Blue Sow Thistle" = "Cicerbita alpina", "Garden Lettuce" = "Lactuca sativa", "White Waterlily" = "Nymphaea alba", "Scarlet Pimpernel" = "Anagallis arvensis", "Ice Plant" = "Mesembryanthemum crystallinum", "Quill FameFlower" = "Phemerantus teretifolius", "Sundrops" = "Oenothera fruticosa")),
                                     hr(),
                                     fluidRow(column(10, verbatimTextOutput("value"))
                                 )
                                 ),
                                 mainPanel(
                                        includeMarkdown("Description.md"))
                                 ))))
```

---

##### BOTANICAL CLOCK, PLOT, Slide 3
###### Vizualization of the Opening and Closing Times of the flowers in alphabetical order. The code had to be wrapped in the command print() on the Shiny server side.

```{r, echo=TRUE}
ggplot(data=Flowers, aes(x=CLOSING,y=OPENING,fill=FLOWER)) +
                geom_bar(position="dodge",stat="identity") +
                ggtitle("Botanical Clock")
```

---

##### BOTANICAL CLOCK, EVEN MORE, Slide 4
###### Nowadays botanical or flower clocks look totally different. In fact these are planted large decorative clocks with the clock face formed by carpet bedding, usually found in a park or other public recreation area. I embedded another Markdown-File called 'More.md' as follows:

```{r}
tabPanel("More",
              mainPanel(
                      fluidRow(
                              column(10,
                                     includeMarkdown("More.md")))))
```

---

#### BOTANICAL CLOCK, PICTURE OF A CURRENT FLOWER CLOCK, Slide 5
###### As the cherry of the pie I finally wanted to show a picture of how a botanical or flower clock looks like nowadays and I added one of Germany as I am a german. Please find all related files hosted in my github repository 'https://github.com/Urli2016/GitHub/tree/master/BotanicalCl_A/BotanicalClockA/BotanicalClockA'.

```{r}
img(class="img-polaroid",
      src=paste0("http://upload.wikimedia.org/",
                 "wikipedia/commons/f/fa/",
                 "Eilenburg_Blumenuhr2.jpg"),
          tags$small("Users own work, Photographed by Joebo7 3rd May 2009",
                  a(href="http://commons.wikimedia.org/wiki/File%3AEilenburg_Blumenuhr2.jpg")))
```

